### 2013-01-24 seminar_talk_october_2011.tex
Initial commit

      \theoremstyle{plain}
      \newtheorem{theorem}{Theorem}
      \newtheorem{lemma}[theorem]{Lemma}
      \newtheorem{corollary}[theorem]{Corollary}
      \newtheorem{proposition}[theorem]{Proposition}
      \newtheorem{conjecture}[theorem]{Conjecture}
      \newtheorem{question}[theorem]{Question}
      \newtheorem{example}[theorem]{Example}

@@

% Strategy uparrow shortcuts
\newcommand{\prewin}{\uparrow_{\text{pre}}}
\newcommand{\markwin}{\uparrow_{\text{mark}}}
\newcommand{\tactwin}{\uparrow_{\text{tact}}}
\newcommand{\ktactwin}[1]{\uparrow_{#1\text{-tact}}}
\newcommand{\kmarkwin}[1]{\uparrow_{#1\text{-mark}}}
\newcommand{\codewin}{\uparrow_{\text{code}}}
\newcommand{\limitwin}{\uparrow_{\text{limit}}}

@@

\centerline{\bf PhD Research Results}
\centerline{Steven Clontz}

@@

\begin{theorem}
$P \not\tactwin D_{K,P}(M)$ where $M$ is the metric fan space.
\end{theorem}

\begin{proof}
Give $P$ the tactic $\sigma$. Suppose that for all $n<\omega$, there is an upper bound $m<\omega$ so that for each $C \in K[M]$, if $\pi_1(\sigma(C))=n$, then $\pi_2(\sigma(C))<m$. We may then define $f(n)=m$, and let $C_f=\{(x,y):f(x)<y\}\in K[M]$. $\sigma(C_f)$ must show a contradiction if $\sigma$ is legal.

So it follows that there is some $n<\omega$ such that there are compact sets $C_i\in K[M]$ with $\pi_1(\sigma(C_i))=n$ and $\pi_2(\sigma(C_i))<\pi_2(\sigma(C_{i+1}))$. The play $\left<C_0,\sigma(C_0),C_1,\sigma(C_1),\dots\right>$ is a counter to $\sigma$.
\end{proof}

@@

It then follows that the closure of $\mathcal{P}$ under finite unions and subsets, along with all finite sets, is an ideal. Its dual filter may then be extended to an ultrafilter $\mathcal{F}$ such that every possible play by $P$ is the complement of some member of $\mathcal{F}$.
\end{proof}

@@

\centerline{\bf Another game: $Con_{O,P}(X,x)$}

\begin{definition} 
Gruenhage's open-point convergence game $Con_{O,P}(X,x)$ has $O$ choosing nested open sets and $P$ choosing a point within the last chosen open set by $O$. $O$ wins if the points chosen by $P$ converge to $x$.
\end{definition}

@@

\begin{proposition}
$O\not\prewin Con_{O,P}(\kappa\cup\{\infty\},\infty)$, where $\kappa\cup\{\infty\}$ is the one-point compactification of discrete $\kappa\geq\omega_1$.
\end{proposition}

\begin{proof}
Given a predetermined strategy $\sigma(n)$ for $O$, $P$ simply chooses any ordinal in $\bigcap_{n<\omega} \sigma(n)$ to play on every turn.
\end{proof}

@@

\begin{proposition}
$O\codewin Con_{O,P}(\kappa\cup\{\infty\},\infty)$ for any cardinal $\kappa$. 
\end{proposition}

@@

\begin{proposition}
$O\not\tactwin Con_{O,P}(\kappa\cup\{\infty\},\infty)$ for $\kappa\geq\omega_1$.
\end{proposition}

\begin{proof}
Let $F(\alpha)$ be the complement of a tactical strategy for $O$. There exists some $n<\omega$ such that we may find an infinite $B\subseteq \omega_1$ with $n\not\in F(\beta)$ for $\beta\in B$ - if not, we may find uncountable ordinals $\alpha$ such that $\omega \subseteq F(\alpha)$, a contradiction. Choose $\beta\in B\setminus F(n)$, and note that repeating $n,\beta$ is a successful counter to $O$'s strategy.
\end{proof}

@@

\begin{theorem}
$O\not\ktactwin{k}Con_{O,P}(\kappa\cup\{\infty\},\infty)$ for $\kappa\geq\omega_1$.
\end{theorem}

\begin{proof}
Let $\sigma:[\omega_1]^{\leq k}\to[\omega_1]^{<\omega}$ be a $k$-tactical strategy for $O$ restricted to $\omega_1$ and $F(S)=\omega_1\setminus\sigma(S)$.

@@

Peter J. Nyikos has shown the following:

\begin{theorem}
$O\not\markwin Con_{O,P}(\omega_1\cup\{\infty\},\infty)$.
\end{theorem}

This can be improved:

\begin{theorem}
$O\not\kmarkwin{k} Con_{O,P}(\kappa\cup\{\infty\},\infty)$ for $\kappa\geq\omega_1$.
\end{theorem}

\begin{proof}
Let $F:[\omega_1]^{\leq k}\times\omega\to[\omega_1]^{<\omega}$ be the complement of a $k$-Markov strategy for $O$ restricted to $\omega_1$.

Let $W_0=\omega_1$. We define $W_\alpha$ recursively as follows:
    \begin{itemize}
    \item For successor ordinals $\alpha+1$, let $\beta$ be the least element of $W_\alpha$ such that \[(\beta,\omega_1) \cap \bigcup_{S\in [\beta]^{\leq k}, n<\omega} F(S,n)\] is nonempty. If no such $\beta$ exists, let $W_{\alpha+1}=W_\alpha$ and otherwise let \[W_{\alpha+1}=W_\alpha \setminus \left((\beta,\omega_1) \cap \bigcup_{S\in[\beta]^{\leq k}, n<\omega} F(S,n)\right)\]
    \item For limit ordinals $\alpha$, let $W_\alpha = \bigcap_{\beta<\alpha} W_\beta$.
    \end{itemize}

Finally let $W=\bigcap_{\alpha<\omega_1}W_\alpha$ and observe that it is unbounded. Let $R$ collect all ordinals $\alpha\in W$ such that there is an ordinal $\beta_\alpha$ and number $n_\alpha<\omega$ where for all $S\in[W\cap(\beta_\alpha,\omega_1)]^{\leq k}$, $\alpha \in F(S,n_\alpha)$.

If $R$ was infinite, then there is $\alpha_i\in R$ for each $i<\omega$ and some $N<\omega$ where for all $S\in[W\cap(\beta_{\alpha_i},\omega_1)]^{\leq k}$, $\alpha_i \in F(S,N)$, and thus for all $S\in[W\cap(\sup \beta_{\alpha_i},\omega_1)]^{\leq k}$,  $\{\alpha_i : i<\omega\} \subset F(S,N)$, a contradiction. So let $0^*$ be the least element of $W\setminus R$.

Now, define a strictly increasing sequence of ordinals $\left<\alpha_1,\alpha_2,\alpha_3,\alpha_4,\dots\right>$ such that $\alpha_i \in W$ and $0^* \not\in F(\{\alpha_{2i+1},\dots,\alpha_{2i+k}\})$ for all $i$. The play $\left<0^*,\alpha_1,\dots,\alpha_k,0^*,\alpha_{k+1},\dots,\alpha_{2k},0^*,\dots\right>$ then defeats the Markov strategy.
\end{proof}

While these counters prevent convergence to $\infty$, they do not prohibit clustering, as any sequence of points with infinite range clusters at $\infty$ in this space.

\begin{definition} 
The open-point clustering game $Clus_{O,P}(X,x)$ has $O$ choosing nested open sets and $P$ choosing a point within the last chosen open set by $O$. $O$ wins if the points chosen by $P$ cluster to $x$.
\end{definition}

Any strategy which forces convergence also forces clustering, so a coding strategy exists for player $O$. And since the counter used above to foil any tactical strategy had only finite range...

\begin{proposition}
$O\not\tactwin Clus_{O,P}(X,\infty)$.
\end{proposition}

The other counters only attempt to repeat a point infinitely often, and may have infinite range.

\begin{example}
For $\omega\leq\alpha<\omega_1$ let $\leq_{\alpha}$ be a well-ordering of $\omega_1$ such that its restriction to $\alpha$ is isomorphic to $\omega$ with isomorphism $f(n):\omega\to\alpha$. For $n<\omega$ let $\leq_n$ simply be $\leq$ and $f$ be the identity.

The 2-tactical strategy for $O$ in $Clus_{O,P}(\omega_1\cup\{\infty\}),\infty)$ whose complement is, for $\alpha<\beta$, $F(\alpha,\beta)=\{\gamma : \gamma \leq_\beta \alpha \} \cup \{\beta\}$, forces the point-picker to chose more than three distinct points.
\end{example}

\begin{proof}
Suppose Player $P$ started with $\alpha_0<\alpha_1$. Player $O$ forbids \[F(\alpha_0,\alpha_1) = \{\gamma : \gamma \leq_{\alpha_1}\alpha_0\} \cup \{\alpha_1\}\] so Player $P$ must respond with $\alpha_2$ such that either $\alpha_0<\alpha_1<\alpha_2$ or $\alpha_0<_{\alpha_1}\alpha_2<\alpha_1$.

In the first case that $\alpha_0<\alpha_1<\alpha_2$, Player $O$ now forbids \[F(\alpha_1,\alpha_2) = \{\gamma : \gamma \leq_{\alpha_2}\alpha_1\} \cup \{\alpha_2\}\] If $\alpha_0<_{\alpha_2}\alpha_1$ we're done. Otherwise, Player $P$ chooses $\alpha_0>_{\alpha_2}\alpha_1$ again, and Player $O$ responds with \[F(\alpha_0,\alpha_2)=\{\gamma : \gamma \leq_{\alpha_2} \alpha_0 \} \cup \{\alpha_2\}\] which successfully forbids $\alpha_1$.

In the second case that $\alpha_0<_{\alpha_1}\alpha_2<\alpha_1$, Player $O$ forbids \[F(\alpha_1,\alpha_2) = \{\gamma : \gamma \leq_{\alpha_1}\alpha_2\} \cup \{\alpha_1\}\] which successfully forbids $\alpha_0$.

Thus, a fourth ordinal must be selected.
\end{proof}

But the fourth ordinal is all that is needed.

\begin{theorem}
$O\not\ktactwin{2}Clus_{O,P}(\omega_1\cup\{\infty\},\infty)$.
\end{theorem}

\begin{proof}
Let $F(\alpha,\beta)$ be the complement of a k-tactical strategy for O, and assume without loss of generality that it does not forbid any ordinals larger than its inputs.

Let $n_0=\min(\omega\setminus F(\emptyset)\setminus F(\omega,\omega+1))$ and $n_1 = \min(\omega\setminus F(n_0)\setminus F(n_0,\omega+1))$.

It follows that $\left<n_0,n_1,\omega,\omega+1,n_0,n_1,\omega,\omega+1,\dots\right>$ is a legal counter.
\end{proof}

But, in fact, a similar counter can be used for any $k$-tactical strategy.

\begin{theorem}
$O\not\ktactwin{k}Clus_{O,P}(\omega_1\cup\{\infty\},\infty)$.
\end{theorem}

\begin{proof}
Let $F(\alpha_0,\dots,\alpha_{k-1})$ be the complement of a k-tactical strategy for O, and assume without loss of generality that it does not forbid any ordinals larger than its inputs.

For $0\leq i < k$, we define \[n_i = \min(\omega\setminus F(n_0,\dots,n_{i-1},\omega+i,\dots,\omega+k-1)\setminus F(n_0,\dots,n_{i-1}))\]

It follows that $\left<n_0,\dots,n_{k-1},\omega,\dots,\omega+k-1,n_0,\dots,n_{k-1},\omega,\dots,\omega+k-1,\dots\right>$ is a legal counter.
\end{proof}

However, a Markov strategy is sufficient to defeat $P$ in the clustering game for $\omega_1$.

\begin{theorem}
$O\markwin Clus_{O,P}(\omega_1\cup\{\infty\},\infty)$.
\end{theorem}

\begin{proof}
For $\omega\leq\alpha<\omega_1$ let $\leq_{\alpha}$ be a well-ordering of $\omega_1$ such that its restriction to $\alpha$ is isomorphic to $\omega$ with isomorphism $f(n):\omega\to\alpha$. For $n<\omega$ let $\leq_n$ simply be $\leq$ and $f$ be the identity.

Let $F(\alpha,n)=\{\gamma : \gamma \leq_\alpha f(n)\}$ be the complement of $O$'s Markov strategy in response to move $\alpha$ in round $n$.

If a legal counter by $P$ does not repeat some largest ordinal infinitely often, it does not result in a win for $P$. Otherwise let $\beta$ be largest ordinal repeated infinitely often in some legal counter by $P$. We note that the forbidden sets responded by $O$ are of the form $F(\beta,n)$ where $n$ increases as the game progresses. It is impossible to repeat any ordinal less than $\beta$ infinitely often due to the increasing round number, so the range of the counter is infinite, and does not result in a win for $P$.
\end{proof}

...while it similarly fails for $\kappa>\omega_1$.

\begin{theorem}
$O\not\kmarkwin{k}Clus_{O,P}(\kappa\cup\{\infty\},\infty)$ for $\kappa>\omega_1$.
\end{theorem}

\begin{proof}
Let $F:\omega\times[\kappa]^{\leq k} \to [\kappa]^\omega$ be the complement of a k-Markov strategy for O, and assume without loss of generality that it does not forbid any ordinals larger than its inputs.

For $0\leq i < k$, we define \[\beta_i = \min(\omega\setminus \bigcup_{n<\omega} F(n,\{\beta_0,\dots,\beta_{i-1},\omega_1+i,\dots,\omega_1+k-1\})\setminus\bigcup_{n<\omega} F(n,\{\beta_0,\dots,\beta_{i-1}\}))\]

It follows that $\left<\beta_0,\dots,\beta_{k-1},\omega_1,\dots,\omega_1+k-1,\beta_0,\dots,\beta_{k-1},\omega_1,\dots,\omega_1+k-1,\dots\right>$ is a legal counter.
\end{proof}

\centerline{\bf $Con_{O,P}(X,x)$ for Sigma Product}

\begin{proposition}
The player $O$ has a winning strategy for $Con_{O,P}(X,x)$ where \[X=\Sigma\mathbb{R}^{\omega_1}=\{x\in \mathbb{R}^{\omega_1}: x_\alpha = 0 \text{ for all but countably many } \alpha<\omega_1\}\]
\end{proposition}

\begin{proof}
Without loss of generality we may assume that $x$ is the zero function. Let $y_n$ be the move by $P$ on turn $n$. For each $y_n$, let $l_n\in \omega_1^{\omega}$ enumerate the nonzero coordinates in $y_n$. Give $O$ the strategy $\sigma(y_0,\dots,y_{n-1}) = \prod_{\alpha<\omega_1} O_\alpha$ where if $\alpha$ is listed in the first $n$ coordinates of any term in $\left<l_k\right>_{k<n}$, then $O_\alpha=(-2^{-n},2^{-n})$, and $O_\alpha=\mathbb{R}$ otherwise.
\end{proof}

\begin{theorem}
For all cardinals $\kappa\leq 2^\omega$, the player $O$ has a winning coding strategy for $Con_{O,P}(X,x)$ where \[X=\Sigma\mathbb{R}^{\kappa}=\{x\in \mathbb{R}^{\kappa}: x_\alpha = 0 \text{ for all but countably many } \alpha<\kappa\}\]
\end{theorem}

\begin{proof}
Note that $|\Sigma\mathbb{R}^\kappa| \leq 2^\omega = |\mathbb{R}|$. Define the following:

    \begin{itemize}
    \item Encode every finite sequence $s$ of functions in $\Sigma\mathbb{R}^{\kappa}$ as a real number $0<r(s)<1$. 
    \item Let $\gamma(U)$ be the function which, for basic open sets $U=\prod_{\alpha<\kappa}U_\alpha$ where $U_0=(-\frac{1}{R},\frac{1}{R})$ for some positive noninteger real number $R$, returns the sequence $r^{-1}(R-\lfloor R\rfloor)$.
    \item Let $n(U)$ be the length of $\epsilon^{-1}(\gamma(U))$.
    \item Let $\psi(U,y)=\epsilon^{-1}(\gamma(U))^\frown\left<y\right>$.
    \item Define $\sigma_0(U,y)$ to be $\left(-\frac{1}{n(U)+r(\psi(U,y))},\frac{1}{n(U)+r(\psi(U,y))}\right)$.
    \item For each $0<\alpha<\kappa$, define the interval $\sigma_\alpha(U,y)$ about $0$ as follows:
        \begin{itemize}
        \item If $\alpha$ is listed in the first $n(U)$ coordinates of any term in the finite sequence $\psi(U,y)$, then $\sigma_\alpha(U,y)=(-\frac{1}{n(U)+1},\frac{1}{n(U)+1})$.
        \item Otherwise, then $\sigma_\alpha(U,y)=\mathbb{R}$.
        \end{itemize}
    \end{itemize}

It follows that $\sigma(U,y)=\prod_{\alpha<\kappa} \sigma_\alpha(U,y)$ is a winning coding strategy.
\end{proof}

\begin{theorem}
For all cardinals $\kappa>2^\omega$ such that $\kappa^\omega = \kappa$, the player $O$ has a winning coding strategy for $Con_{O,P}(X,x)$ where \[X=\Sigma\mathbb{R}^{\kappa}=\{x\in \mathbb{R}^{\kappa}: x_\alpha = 0 \text{ for all but countably many } \alpha<\omega_1\}\]
\end{theorem}

\begin{proof}
Note that $|\Sigma\mathbb{R}^\kappa| = \kappa^\omega = \kappa$. Define the following:

    \begin{itemize}
    \item Encode every finite sequence $s$ of functions in $\Sigma\mathbb{R}^{\kappa}$ as an ordinal $\epsilon(s)<\kappa$. 
    \item Let $\gamma(U)$ be the function which, for basic open sets $U=\prod_{\alpha<\kappa}U_\alpha$ with a unique factor $U_{\alpha^*}$, returns $\alpha^*$.
    \item Let $n(U)$ be the length of $\epsilon^{-1}(\gamma(U))$.
    \item Let $\psi(U,y)=\epsilon^{-1}(\gamma(U))^\frown\left<y\right>$.
    \item For each $\alpha<\kappa$, define the interval $\sigma_\alpha(U,y)$ about $0$ as follows:
        \begin{itemize}
        \item If $\alpha$ is listed in the first $n(U)$ coordinates of any term in the finite sequence $\psi(U,y)$ and is not equal to $\epsilon(\psi(U,y))$, then $\sigma_\alpha(U,y)=(-\frac{1}{n(U)+1},\frac{1}{n(U)+1})$.
        \item If $\alpha=\epsilon(\psi(U,y))$, then $\sigma_\alpha(U,y)=(-\frac{1}{n(U)+2},\frac{1}{n(U)+2})$.
        \item Otherwise, then $\sigma_\alpha(U,y)=\mathbb{R}$.
        \end{itemize}
    \end{itemize}

It follows that $\sigma(U,y)=\prod_{\alpha<\kappa} \sigma_\alpha(U,y)$ is a winning coding strategy.
\end{proof}

% NOPE
%\begin{theorem}
%For all cardinals $\kappa$ such that $2^\omega< \kappa < \kappa^\omega$, the player $O\not\codewin Cl_{O,P}(X,x)$ where \[X=\Sigma\mathbb{R}^{\kappa}=\{x\in% \mathbb{R}^{\kappa}: x_\alpha = 0 \text{ for all but countably many } \alpha<\omega_1\}\]
%\end{theorem}
%
%\begin{proof}We begin by noting that $|\tau|=\kappa<\kappa^\omega$, where $\tau$ is the topology of $\Sigma \mathbb{R}^\kappa$.
%
%Suppose that for all $S\subseteq \Sigma\mathbb{R}^\kappa$ such that $\sigma(U,x)=\sigma(V,y)$ for all $x,y\in\Sigma \mathbb{R}^\kappa$ and $U,V\in\tau$, it follows that $|S|<\kappa^\omega$. Then \[\left|\bigcup_{V\in\tau}\sigma^{-1}(V)\right|=\max(\{\lambda : \lambda=|\tau| \,\vee\, \exists V\in\tau(\lambda=|\sigma^{-1}(V)|)\}) < \kappa^\omega \] while $\bigcup_{V\in\tau}\sigma^{-1}(V)=\tau\times \Sigma\mathbb{R}^\kappa$, a contradiction.
%
%It follows that we may find $S\subseteq \Sigma\mathbb{R}^\kappa$ with $|S|=\kappa^\omega$ such that $\sigma(U,x)=\sigma(V,y)$ for all $x,y\in\Sigma \mathbb{R}^\kappa$ and $U,V\in\tau$.
%
%If $P$ only plays sequences in $S$, then $O$ plays the same set in every round following the initial round. As such, $O$ only places restrictions on $\omega$-many coordinates of the sequences chosen by $P$ throughout the game. Call these restricted coordinates $R\subseteq \kappa$. If $x(\alpha)=0$ for all $x\in S$ and $\alpha\not\in R$, then it would follow that $|S|=|\mathbb{R}|^{|R|}=2^\omega<\kappa^\omega$, a contradiction.
%
%So, choose $x\in S$ such that $x(\alpha)\not=0$ for some $\alpha\not\in R$. The play \[\left<U_0,x,U_1=\sigma(U_0,x),x,U_2=\sigma(U_1,x)=U_1,x,U_1,x,\dots\right>\] is a counter to $\sigma$.
%\end{proof}

\centerline{\bf Finite Countable Game}

\begin{theorem}
Let $\kappa$ be a cardinal such that there exists a function $f:\kappa\to[\kappa]^{\leq \omega}$ where for every $W\in[\kappa]^{\leq\omega}$ there exists $\alpha_W<\kappa$ with $W\subseteq f(\alpha_W)$. Then $F \codewin PF_{F,C}(\kappa)$ and $O \codewin Con_{O,P}(\Sigma\mathbb{R}^\kappa)$.
\end{theorem}

\begin{proof}
Long version.

We begin by defining a few helpful tools. Assume $N\in[\kappa]^{<\omega}$ and $W \in [\kappa]^{\leq\omega}$.
    \begin{itemize}
    \item Let $N^* = N \setminus \{\max(N)\}$.
    \item Noting that $\kappa\setminus \alpha$ is order-isomorphic to $\kappa$ for all $\alpha<\kappa$, let $\gamma_N<\kappa$ be the ordinal mapping to $\max(N)$ in $\kappa\setminus(\max(N^*)+1)$ by the appropriate order isomorphism.
    \item Let $s: [\kappa]^{<\omega} \to \kappa$ be a bijection.
    \item Define $W\restriction n \in [\kappa]^{<\omega}$ so that $W\restriction n \subseteq W\restriction (n+1)$ and $\bigcup_{n<\omega}W\restriction n = W$.
    \item Let $t_N=\max(N\cap\omega)+2$.
    \end{itemize}

Let the (non-winning) coding strategy $\sigma'$ be defined as follows: \[\sigma'(N,W)=\bigcup_{\alpha \in s^{-1}(\gamma_N)} f(\alpha) \restriction t_N\]

Let $\left<N_0,N_1,\dots\right>$ be a play by $F$ following the considered strategy in response to the play $\left<W_0,W_1,\dots\right>$ by $C$ in the game $PF_{F,C}(\kappa)$. (For technical reasons, assume $N_0$ contains at least two ordinals.) This coding strategy could have been a winning strategy for $F$ if it had only satisfied two requirements:

    \begin{enumerate}
    \item First, $s^{-1}(\gamma_{N_k})$ provided ordinals $\{\alpha_{W_0},\dots,\alpha_{W_{k-1}}\}$. (Thus $N_{k+1}=\bigcup_{\alpha \in s^{-1}(\gamma_{N_k})} f(\alpha) \restriction t_{N_k} = \bigcup_{0\leq m < k} f(\alpha_{W_m}) \restriction t_{N_k}$.)
    \item In addition, $t_{N_k} \to \infty$. (Thus $\bigcup_{k<\omega} N_{k+1} = \bigcup_{k<\omega}\bigcup_{0\leq m < k-1} f(\alpha_{W_m}) \restriction t_{N_k} = \bigcup_{m<\omega} f(\alpha_{W_m}) \supseteq \bigcup_{m<\omega} W_m$.)
    \end{enumerate}

We shall improve $\sigma'$ so that it does satsify those requirements, beginning with the second.  Define $\sigma^*$: \[\sigma^*(N,W)=t_N \cup \sigma'(N,W)\] Note then that $t_{N_{k+1}}\geq t_{t_{N_k}} = \max(t_{N_k})+2 = t_{N_k}-1+2=t_{N_k}+1$.

Lastly, to cover the first requirement, we define $\sigma$: \[\sigma(N,W) = \sigma^*(N,W) \cup \{ \max(\sigma^*(N,W))+1+s(s^{-1}(\gamma_N)\cup\{\alpha_W\}) \}\] By induction \[s^{-1}(\gamma_{N_{k+1}}) = s^{-1}(s(s^{-1}(\gamma_{N_k})\cup\{\alpha_{W_k}\})) = s^{-1}(\gamma_{N_k})\cup\{\alpha_{W_k}\} = \{\alpha_{W_0},\dots,\alpha_{W_{k-1}}\}\cup\{\alpha_{W_k}\}\] we see the first requirement is satisfied.

Finally, we turn our attention to $Con_{O,P}(\Sigma\mathbb{R}^\kappa)$. We define the winning strategy $\tau(U,p)$ for $O$ as follows: let $N(U)$ be the non-$\mathbb{R}$ coordinates in the basic open set $U$ and $W(p)$ be the non-$0$ coordinates in $p$. Then $\tau(U,p) = \left(\prod_{\alpha<\kappa} U_\alpha\right) \cap \Sigma\mathbb{R}^\kappa$ where if $\alpha \in \sigma(N(U),W(p))$ then $U_\alpha = (-1/t_{N(U)},1/t_{N(U)})$ and $U_\alpha=\mathbb{R}$ otherwise.
\end{proof}

\begin{proof}
Short version, per GG's suggestion.

Let $W\restriction n \in [\kappa]^n$ be a subset of $W\in[\kappa]^\omega$ such that $W\restriction n \subset W \restriction (n+1)$ and $\bigcup_{n<\omega} W\restriction n = W$.

Define \[\sigma(N,W) = N \cup (|N|+1) \cup \{\alpha_W\} \cup \bigcup_{\alpha \in N} f(\alpha) \restriction |N|\]

Consider the play $\left<\emptyset,W_0,N_1,W_1,N_2,W_2,\dots\right>$ with $F$ following the strategy $\sigma$. Let $\gamma \in W_i$, and note $\gamma \in f(\alpha_{W_i})$ (and $\gamma \in f(\alpha_{W_i})\restriction |N_n|$ for sufficiently large $n$). \[N_{i+1} = \sigma(N_i,W_i) \supseteq \{\alpha_{W_i}\}\] and thus \[N_{n+1} = \sigma(N_n,W_n) \supseteq \bigcup_{\alpha \in N_n} f(\alpha) \restriction |N_n| \supseteq \bigcup_{\alpha \in N_{i+1}} f(\alpha) \restriction |N_n| \supseteq f(\alpha_{W_i}) \restriction |N_n|\] showing $\gamma \in N_{n+1}$. Since $\gamma$ is forbidden in round $n+1$, $\gamma$ appears in finitely many sets chosen by $C$.

We turn our attention to $Con_{O,P}(\Sigma\mathbb{R}^\kappa)$. We define the winning strategy $\tau(U,p)$ for $O$ as follows: let $N(U)$ be the non-$\mathbb{R}$ coordinates in the basic open set $U$ and $W(p)$ be the non-$0$ coordinates in $p$. Then $\tau(U,p) = \left(\prod_{\alpha<\kappa} U_\alpha\right) \cap \Sigma\mathbb{R}^\kappa$ where if $\alpha \in \sigma(N(U),W(p))$ then $U_\alpha = (-\frac{1}{|N(U)|},\frac{1}{|N(U)|})$ and $U_\alpha=\mathbb{R}$ otherwise.

Consider the play $\left<\emptyset,p_0,U_1,p_1,U_2,p_2,\dots\right>$ with $O$ following the strategy $\tau$. Observe that $N(\tau(U,p))=\sigma(N(U),W(p))$. Thus $p_i(\gamma)\not=0$ is equivalent to $\gamma \in W(p_i)$, and by the above argument, for sufficiently large $n$, $\gamma \in \sigma(N(U_n),W(p_n))$. Therefore from round $n$ onward the $\gamma$-coordinates of points chosen by $P$ must lay in $(-\frac{1}{|N(U)|},\frac{1}{|N(U)|})$ and converge to $0$.
\end{proof}

%
%\begin{theorem}
%For all cardinals $\kappa \geq \omega$, the player $F \not\tactwin Cov_{F,C}(\kappa)$.
%\end{theorem}
%
%\begin{proof}
%(Based on Scheeper's Meager Nowhere Dense Games I)
%
%Suppose $\sigma$ is a tactical strategy for $F$ such that (without loss of generality) the first move is $\emptyset$. Let $A=\{2n: n<\omega\}$ and $B=\{2n+1:n<\omega\}$.
%
%By Todorcevic's Partition Relations for Partially Ordered Sets, $\mathcal{P}(A)\rightarrow(\omega)^1_B$. That is, for any function $\Phi$ from $\mathcal{P}(A)$ to $B$, there is some $b_\Phi\in B$ and $X_0\subseteq X_1\subseteq \dots \in \mathcal{P}(A)$ such that $\Phi(X_i)=b_\Phi$ for all $i$. Define $\Phi:\mathcal{P}(A)\rightarrow B$ such that $\Phi(X)\in B\setminus(\sigma(B\cup X))$.
%
%Observe the play $\left<\emptyset, B\cup X_0, \sigma(B\cup X_0), B \cup X_1, \sigma(B \cup X_1), B \cup X_2, \dots \right>$. As $b_\Phi \in B \subseteq \bigcup_{i<\omega} B \cup X_i$ but $b_\Phi \not\in \bigcup_{i<\omega} \sigma(B\cup X_i)$, this is a successful counter to any tactic by $F$.
%\end{proof}
%
%\begin{proposition}
%For all cardinals $\kappa \geq \omega_1$, the player $F \not\markwin Cov_{F,C}(\kappa)$.
%\end{proposition}
%
%\begin{proof}
%Suppose $\sigma$ is a Markov strategy for $F$ such that (without loss of generality) the first move is $\emptyset$. Let $A,B\in\mathcal{P}(\kappa)$ be disjoint with $|A|=|B|\geq\omega_1$.
%
%By Todorcevic's Partition Relations for Partially Ordered Sets, $\mathcal{P}(A)\rightarrow(\omega)^1_B$. That is, for any function $\Phi$ from $\mathcal{P}(A)$ to $B$, there is some $b_\Phi\in B$ and $X_0\subseteq X_1\subseteq \dots \in \mathcal{P}(A)$ such that $\Phi(X_i)=b_\Phi$ for all $i$. Define $\Phi:\mathcal{P}(A)\rightarrow B$ such that $\Phi(X)\in B\setminus(\bigcup_{n<\omega}\sigma(B\cup X,n))$.
%
%Observe the play $\left<\emptyset, B\cup X_0, \sigma(B\cup X_0,1), B \cup X_1, \sigma(B \cup X_1,2), B \cup X_2, \dots \right>$. As $b_\Phi \in B \subseteq \bigcup_{i<\omega} B \cup X_i$ but $b_\Phi \in \bigcap_{m<\omega} B \setminus (\bigcup_{n<\omega}\sigma(B\cup X_m,n))$ implying $b_\Phi \not\in \bigcup_{m<\omega}\sigma(B\cup X_m,m+1)$, this is a successful counter to any Markov strategy by $F$.
%\end{proof}

>>>>

      \theoremstyle{plain}
      \newtheorem{theorem}{Theorem}
      \newtheorem{lemma}[theorem]{Lemma}
      \newtheorem{corollary}[theorem]{Corollary}
      \newtheorem{proposition}[theorem]{Proposition}
      \newtheorem{conjecture}[theorem]{Conjecture}
      \newtheorem{question}[theorem]{Question}

@@

% Strategy uparrow shortcuts
\newcommand{\prewin}{\uparrow_{\text{pre}}}
\newcommand{\markwin}{\uparrow_{\text{mark}}}
\newcommand{\tactwin}{\uparrow_{\text{tact}}}
\newcommand{\ktactwin}[1]{\uparrow_{#1\text{-tact}}}
\newcommand{\codewin}{\uparrow_{\text{code}}}

@@

\centerline{\bf Topology Seminar Talk - Late October / Early Novemeber 2011}
\centerline{Steven Clontz}

@@

@@

It then follows that the closure of $\mathcal{P}$ under finite unions and subsets is an ideal. Its dual filter may then be extended to an ultrafilter $\mathcal{F}$ such that every possible play by $P$ is the complement of some member of $\mathcal{F}$.
\end{proof}

@@

\centerline{\bf Another game: $G_{O,P}(X,x)$}

\begin{definition} 
Gruenhage's open-point convergence game $G_{O,P}(X,x)$ has $O$ choosing nested open sets and $P$ choosing a point within the last chosen open set by $O$. $O$ wins if the points chosen by $P$ converge to $x$.
\end{definition}

@@

\begin{proposition}
$O\not\prewin G_{O,P}(\omega_1\cup\{\infty\},\infty)$, where $\omega_1\cup\{\infty\}$ is the one-point compactification of discrete $\omega_1$.
\end{proposition}

\begin{proof}
Given a predetermined strategy $\sigma(n)$ for $O$, $P$ simply chooses any ordinal in $\bigcup_n \sigma(n)$ to play on every turn.
\end{proof}

@@

\begin{proposition}
$O\codewin G_{O,P}(\omega_1\cup\{\infty\},\infty)$. 
\end{proposition}

@@

\begin{theorem}
$O\not\tactwin G_{O,P}(\omega_1\cup\{\infty\},\infty)$.
\end{theorem}

\begin{proof}
Let $\sigma(\alpha)$ be a tactical strategy for $O$ and $F(\alpha)=\omega_1\setminus\sigma(\alpha)$. Suppose by way of contradiction that for all $\alpha_0,\alpha_1<\omega_1$, if $\alpha_1 \not\in F(\alpha_0)$ then it follows that $\alpha_0\in F(\alpha_1)$. Then for all $\alpha<\omega_1$, $\alpha\in F(\beta)$ for all $\beta\not\in F(\alpha)$.

So $0\in F(\beta)$ for all $\beta\not\in F(0)$, $1\in F(\beta)$ for all $\beta \not\in F(1)$, and so on. Then $0,1,2,\dots\in F(\beta)$ for all $\beta\not\in\bigcup_n F(n)\not=\omega_1$, contradiction.

Thus there exist a pair $\alpha_0,\alpha_1$ such that $\alpha_1\not\in F(\alpha_0)$ and $\alpha_0\not\in F(\alpha_1)$. $P$ beats $\sigma$ by playing this pair repeatedly.
\end{proof}

@@

\begin{theorem}
$O\not\ktactwin{k}G_{O,P}(\omega_1\cup\{\infty\},\infty)$.
\end{theorem}

\begin{proof}
Let $\sigma:[\omega_1]^{\leq k}\to[\omega_1]^{<\omega}$ be a $k$-tactical strategy for $O$ and $F(S)=\omega_1\setminus\sigma(S)$.

@@

Dr. Gruenhage tells me Peter J. Nyikos has shown the following:

\begin{theorem}
$O\not\markwin G_{O,P}(\omega_1\cup\{\infty\},\infty)$.
\end{theorem}

It is natural to ask:

\begin{question}
Does $O$ have a winning strategy which uses only the turn number and the last $k$ moves of $P$ for the game $G_{O,P}(\omega_1\cup\{\infty\},\infty)$? (Probably not.)
\end{question}
